% chap11sec08

\section{Integration of complex functions}

Suppose $f$ is a complex-valued function defined on a measure space $X$,
and $f = u + iv$,
where $u$ and $v$ are real.
We say that $f$ is measurable if and only if
both $u$ and $v$ are measurable.

It is easy to verify that sums and products of complex measurable functions
are again measurable. Since
\begin{equation*}
    \left| f \right| = (u^2 + v^2)^{1/2},
\end{equation*}
Theorem \ref{thm:11.18} shows that $|f|$ is measurable for every complex measurable $f$.

Suppose $\mu$ is a measure on $X$,
$E$ is a measurable subset of $X$,
and $f$ is a complex function on $X$.
We say that $f \in \mathscr{L}(\mu)$ on $E$ provided that $f$ is measurable
and
\begin{equation}
    \label{eq:11.97}
    \int_E \left| f \right| \d \mu < +\infty ,
\end{equation}
and we define
\begin{equation*}
    \int_E f \d \mu =
    \int_E u \d \mu + i
    \int_E v \d \mu
\end{equation*}
if (\ref{eq:11.97}) holds.
Since $|u| \leq |f|$, $|v| \leq |f|$, and $|f | \leq | u | + | v |$,
it is clear that
(\ref{eq:11.97}) holds if and only if $u \in \mathscr{L}(\mu)$ and $v \in \mathscr{L}(\mu)$ on $E$.

Theorems \ref{myremark:11.23}(a), (d), (e), (f), \ref{thm:11.24}(b), \ref{thm:11.26}, \ref{thm:11.27}, \ref{thm:11.29}, and \ref{thm:11.32}
can now be extended to Lebesgue integrals of complex functions.
The proofs are quite straightforward.
That of Theorem \ref{thm:11.26} is the only one that offers
anything of interest:

If $f \in \mathscr{L}(\mu)$ on $E$, there is a complex number $c$, $|c| = 1$, such that
\begin{equation*}
    c \int_E f \d \mu \geq 0 .
\end{equation*}
Put $g = cf = u + iv$, $u$ and $v$ real.
Then
\begin{equation*}
    \left| \int_E f \d \mu \right| =
    c \int_E f \d \mu =
    \int_E g \d \mu =
    \int_E u \d \mu \leq
    \int_E | f | \d \mu .
\end{equation*}
The third of the above equalities holds since the preceding ones show that
$\int f \d \mu$ is real.
