\section{Introduction}
First we use $\sqrt{2}$ to construct real number system from integer and rational numbers.

\begin{myExample}
    \label{Example:1.1}
    \begin{equation}
        \label{eq:1.1}
        p^2=2
    \end{equation}
    $p$ is not a rational number.
\end{myExample}

\begin{proof}
    If $p$ is rational,  $\exists m,n \in \mathbf{N}$, 
    s.t. $p=m/n$. $\gcd (m,n) = 1$.
    Then \ref{eq:1.1}
    \begin{equation}
        \label{eq:1.2}
        m^2 = 2n^2.
    \end{equation}

    $m$ is even, $m = 2k$.
    Then $(2k)^2 = 2n^2$, $2k^2 = n^2$, $k$ is even, $\gcd (m,n)=2\neq 1$,
    contrary to our choice of $m$ and $n$. Hence p can't be a rational number.
\end{proof}

After proving $\sqrt{2}$ isn't a rational number, rudin use $\sqrt{2}$ to divide the rationals

\mybox{在证明 $\sqrt{2}$ 不是有理数后, 使用 $\sqrt{2}$ 将有理数集分成两部分.  引出了分划的概念? }

\begin{align*}
    A = \{p|p^2<2\}\\
    B = \{p|p^2>2\}
\end{align*}
$A$ \emph{contains no largest number},\\
$B$ \emph{contains no smallest number}.\\
$\forall p\in A$, $\exists q\in A$, s.t. $p<q$,\\
$\forall p\in B$, $\exists q\in B$, s.t. $p>q$,\\
$\forall p>0$
\begin{equation}
    \label{eq:1.3}
    q = p-\frac{p^2-2}{p+2} = \frac{2p+2}{p+2}
\end{equation}

Then 
\begin{equation}
    \label{eq:1.4}
    q^2 - 2 = \frac{2(p^2-2)}{(p+2)^2}
\end{equation}

If $p\in A$, $p^2<2$. \ref{eq:1.3} shows that $q>p$, \ref{eq:1.4} shows that $q^2<2$, $q\in A$.

If $p\in B$, $p^2>2$. \ref{eq:1.3} shows that $q<p$, \ref{eq:1.4} shows that $q^2>2$, $q\in B$.


\begin{myRemark}
    \label{Remark:1.2}
    The purpose of the above discussion has been to show that 
    the rational number system has {\color{red}certain gaps}, 
    in spite of the fact that between any two rationals there is another: 
    If $r<s$ then $r<(r+s)/2<s$.
    The real number system fills these gaps.
    This is the principal reason for the fundamental role which it plays in analysis.
\end{myRemark}

\mybox{
    有理数的稠密性与实数的连续性. 
    在分析中, 考察极限等需要的是数系的连续性, 因此需要先建立实数系. 
    事实上, 我们是先有微积分, 后有实数理论的. \\
    三次数学危机:无理数, 微积分基础, 集合论
    实数理论是极限的基础. 
}

In order to elucidate its structure, as well as that of the complex numbers, 
we start with a brief discussion of the general concepts of \emph{ordered set} and \emph{field}.

\mybox{
    rudin引入复数的方法非常怪, 对初学者非常不友好, 过于抽象了. 
    想起一个法国笑话, 问小学生$2+3$等于几, 回答 $2+3=3+2$ 加法是一个交换群（Abel 群）...
} 

Here is some of the standard set-theoretic terminology that will be used throughout this book.

\mybox{接下来引入一些集合论的定义}

\begin{myDef}
    \label{myDef:1.3}
    If $A$ is any set (whose elements may be numbers or any other objects), 
    we write $x\in A$ to indicate that $x$ is a member (or an element) of $A$.
    \mybox{
        element 还没定义\\    
        object指代什么? 我个人认为集合理解的难点在于集合的集合. 
        % 这一点可以引出罗素悖论
        }
    If $x$ is not a member of $A$, we write: $x\notin A$.

    \emph{empty set} $\varnothing$ contains no element, If a set has at least one element, it is called \emph{nonempty}.

    $A,B$ are sets, 
    $\forall x\in A$, $x\in B$, we say that $A$ is a \emph{subset} of $B$, $A \subset B$ or $B \supset A$. 
    If $\exists x\in B$, $x\notin A$, A is a \emph{proper subset} of $B$, $A \subsetneqq B$.
    Note that $A\subset A$ for every set $A$.

    (Bernstein) If $A\subset B$ and $B\subset A$, we write $A = B$. Otherwise $A \neq B$.
\end{myDef}
\mybox{这条性质在证明集合相等时很常用}

\begin{myDef}
    \label{myDef:1.4}
    Throughout Chap. 1, the set of all rational numbers will be denoted by $\Q $.
\end{myDef}