% chap11sec04

\section{Measurable functions}

\begin{mydef}
    \label{def:11.13}
    measurable function
    \begin{equation}
        \label{eq:11.42}
        \{x|f(x) > a\}
    \end{equation}
    is measurable for every real $a$.
\end{mydef}

\begin{myExample}
    If $X = \R^P$ and $\mathfrak{M} = \mathfrak{M}(\mu)$ 
    % (µ) 
    as defined in Definition \ref{def:11.9}, every continuous $f$ is measurable, since then (\ref{eq:11.42}) is an open set.
\end{myExample}

\begin{thm}
    \label{thm:11.15}
    Each of the following four conditions implies the other three:
    \begin{enumerate}[(a)]
        \item $\{x|f(x) >    a\}$ is measurable for every real $a$.
        \item $\{x|f(x) \geq a\}$ is measurable for every real $a$.
        \item $\{x|f(x) <    a\}$ is measurable for every real $a$.
        \item $\{x|f(x) \leq a\}$ is measurable for every real $a$.
    \end{enumerate}
\end{thm}

\begin{thm}
    \label{thm:11.16}
    If $f$ is measurable, then $\left| f \right|$ is measurable. 
\end{thm}

\begin{proof}
    \begin{equation*}
        \{x | \left| f(x) \right| < a\} = 
        \{x | f(x) <  a\} \cap 
        \{x | f(x) > -a\} .
    \end{equation*}
\end{proof}

\begin{thm}
    \label{thm:11.17}
    Let $\{f_n\}$ be a sequence of measurable functions. 
    For $x \in X$, put
    \begin{align*}
        g(x) &= \sup f_n(x) \quad (n=1,2,3,\dots), \\
        f(x) &= \limsup_{n \rightarrow \infty} f_n (x) .
    \end{align*}
    Then $g$ and $h$ are measurable.
\end{thm}

The same is of course true of the $\inf$ and $\liminf$.

\begin{proof}
    \begin{align*}
        \{x | g(x) > a\} &= \bigcup_{n=1}^{\infty} \{x | f_n(x) > a\} , \\
        h(x) &= \inf g_m (x),
    \end{align*}
    where $g_m (x) = \sup f_n (x) (n \geq m)$.
\end{proof}

\begin{myCorollary*}
    \begin{asparaenum} [(a)]
        \item If $f$ and $g$ are measurable, then $\max(f, g)$ and $\min(f, g)$ are measurable. 
        If
        \begin{equation}
            \label{eq:11.47}
            f^+ =  \max (f, 0), \quad
            f^- = -\min (f, 0),
        \end{equation}
        it follows, in particular, that $f^+$ and $f^-$ are measurable.
        \item The limit of a convergent sequence of measurable functions is measurable.
    \end{asparaenum}
\end{myCorollary*}

\begin{thm}
    \label{thm:11.18}
    Let $f$ and $g$ be measurable real-valued functions defined on $X$,
    let $F$ be real and continuous on $\R^2$ , and put
    \begin{equation*}
        h(x) = F(f (x), g(x))
        \quad (x \in X)
    \end{equation*}
    Then $h$ is measurable.

    In particular, $f + g$ and $fg$ are measurable.
\end{thm}

