% chap00
\chapter*{Preface}

This book is intended to serve as a text for the course in analysis that is usually
taken by advanced undergraduates or by first-year students who study mathematics.

The present edition covers essentially the same topics as the second one,
with some additions, a few minor omissions, and considerable rearrangement. I hope that these changes will make the material more accessible amd more attractive to the students who take such a course.

Experience has convinced me that it is pedagogically unsound (though
logically correct) to start off with the construction of the real numbers from the
rational ones. At the beginning, most students simply fail to appreciate the need
for doing this. Accordingly, the real number system is introduced as an ordered
field with the least-upper-bound property, and a few interesting applications of
this property are quickly made. However, Dedekind's construction is not omitted. It is now in an Appendix to Chapter I, where it may be studied and enjoyed
whenever the time seems ripe.

The material on functions of several variables is almost completely rewritten, with many details filled in, and with more examples and more motivation. The proof of the inverse function theorem---the key item in Chapter 9---is
simplified by means of the fixed point theorem about contraction mappings.
Differential forms are discussed in much greater detail. Several applications of
Stokes' theorem are included.

As regards other changes, the chapter on the Riemann-Stieltjes integral
has been trimmed a bit, a short do-it-yourself section on the gamma function
has been added to Chapter 8, and there is a large number of new exercises, most
of them with fairly detailed hints.

I have also included several references to articles appearing in the \emph{American Mathematical Monthly} and in \emph{Mathematics Magazine}, in the hope that students
will develop the habit of looking into the journal literature. Most of these
references were kindly supplied by R. B. Burckel.

Over the years, many people, students as well as teachers, have sent me
corrections, criticisms, and other comments concerning the previous editions
of this book. I have appreciated these, and I take this opportunity to express
my sincere thanks to all who have written me.


WALTER RUDIN
