\section{Introduction}
First we use $\sqrt{2}$ to construct real number system from integer and rational numbers.

\begin{newexample}
    \label{newexample:1.1}
    \begin{equation}
        \label{eq:1.1}
        p^2=2
    \end{equation}
    $p$ is not a rational number.
\end{newexample}

\begin{proof}
    If $p$ is rational,  $\exists m,n \in \mathbf{N}$, 
    s.t. $p=m/n$. $\gcd (m,n) = 1$.
    Then \ref{eq:1.1}
    \begin{equation}
        \label{eq:1.2}
        m^2 = 2n^2.
    \end{equation}

    $m$ is even, $m = 2k$.
    Then $(2k)^2 = 2n^2$, $2k^2 = n^2$, $k$ is even, $\gcd (m,n)=2\neq 1$,
    contrary to our choice of $m$ and $n$. Hence p can't be a rational number.
\end{proof}

After proving $\sqrt{2}$ isn't a rational number, rudin use $\sqrt{2}$ to divide the rationals

\mybox{在证明 $\sqrt{2}$ 不是有理数后, 使用 $\sqrt{2}$ 将有理数集分成两部分.  引出了分划的概念? }

\begin{align*}
    A = \{p|p^2<2\}\\
    B = \{p|p^2>2\}
\end{align*}
$A$ \emph{contains no largest number},\\
$B$ \emph{contains no smallest number}.\\
$\forall p\in A$, $\exists q\in A$, s.t. $p<q$,\\
$\forall p\in B$, $\exists q\in B$, s.t. $p>q$,\\
$\forall p>0$
\begin{equation}
    \label{eq:1.3}
    q = p-\frac{p^2-2}{p+2} = \frac{2p+2}{p+2}
\end{equation}

Then 
\begin{equation}
    \label{eq:1.4}
    q^2 - 2 = \frac{2(p^2-2)}{(p+2)^2}
\end{equation}

If $p\in A$, $p^2<2$. \ref{eq:1.3} shows that $q>p$, \ref{eq:1.4} shows that $q^2<2$, $q\in A$.

If $p\in B$, $p^2>2$. \ref{eq:1.3} shows that $q<p$, \ref{eq:1.4} shows that $q^2>2$, $q\in B$.


\begin{myremark}
    \label{myremark:1.2}
    The purpose of the above discussion has been to show that 
    the rational number system has \myKeywordred{certain gaps}, 
    in spite of the fact that between any two rationals there is another: 
    If $r<s$ then $r<(r+s)/2<s$.
    The real number system fills these gaps.
    This is the principal reason for the fundamental role which it plays in analysis.
\end{myremark}

\mybox{
    有理数的稠密性与实数的连续性. 
    在分析中, 考察极限等需要的是数系的连续性, 因此需要先建立实数系. 
    事实上, 我们是先有微积分, 后有实数理论的. \\
    三次数学危机:无理数, 微积分基础, 集合论
    实数理论是极限的基础. 
}

In order to elucidate its structure, as well as that of the complex numbers, 
we start with a brief discussion of the general concepts of \myKeywordblue{ordered set} and \myKeywordblue{field}.

% \mybox{
%     rudin引入复数的方法非常怪, 对初学者非常不友好, 过于抽象了. 
%     % 想起一个法国笑话, 问小学生$2+3$等于几, 回答 $2+3=3+2$ 加法是一个交换群（Abel 群）...
% } 

Here is some of the standard set-theoretic terminology that will be used throughout this book.

% \mybox{接下来引入一些集合论的概念}

\mybox{这里未经定义就使用了集合 Set 的概念

Set  \url{https://mathworld.wolfram.com/Set.html}

A set is a finite or infinite collection of objects 
in which order has no significance, 
and multiplicity is generally also ignored 
(unlike a list or multiset). 
Members of a set are often referred to as elements 
and the notation $a \in A$ is used to denote that 
$a$ is an element of a set $A$. 
The study of sets and their properties is the object of set theory.

Older words for set include aggregate and set class. 
Russell also uses the unfortunate term manifold to refer to a set.

Historically, 
a single horizontal overbar was used to denote 
a set stripped of any structure besides order, 
and hence to represent the order type of the set. 
A double overbar indicated stripping the order from the set 
and hence represented the cardinal number of the set. 
This practice was begun by set theory founder Georg Cantor.

Symbols used to operate on sets include 
intersection $\cap$ (which means "and" or intersection), 
and union $\cup$ (which means "or" or union). 
The symbol emptyset $\varnothing$ is used to denote 
the set containing no elements, called the empty set.

There are a number of different notations related to the theory of sets. 
In the case of a finite set of elements,
one often writes the collection inside curly braces, e.g.,
\[A={1,2,3}\]
}

%  too long notes out side box

% for the set of natural numbers less than or equal to three. Similar notation can be used for infinite sets provided that ellipses are used to signify infiniteness, e.g.,
% \[B={3,4,5,...} 	\]

% for the collection of natural numbers greater than or equal to three, or
% \[C={...,-4,-2,0,2,4,...} 	\]

% for the set of all even numbers.

% In addition to the above notation, one can use so-called set builder notation to express sets and elements thereof. The general format for set builder notation is
% \[{x:p(x)}, 	\]

% where $x$ denotes an element and $p(x)$ denotes a property $p$ satisfied by $x$. $()$ can also be expanded so as to indicate construction of a set which is a subset of some ambient set $X$, e.g.,
% \[{x \in X:p(x)}. 	\]



% It is worth noting is that the "$:$" in $()$ and $()$ is sometimes replaced by a vertical line, e.g.,
% \[{x \in X|p(x)}. 	\]
% Also worth noting is that the sets in $()$, $()$, and $()$ can all be rewritten in set builder notation as subsets of the set Z of integers, namely
% \begin{align*}
%     A	&=	{n \in N:n<=3}	\\
%     B	&=	{n \in N:n>=3}	\\
%     C	&=	{n \in Z:n\text{ is even}},	
% \end{align*}
% respectively.

\mybox{

Other common notations related to set theory include $A^B$, which is used to denote the set of maps from $B$ to $A$ where $A$ and $B$ are arbitrary sets. 
For example, an element of $X^\N$ would be a map from the natural numbers $\N$ to the set $X$. 
Call such a function $f$, then $f(1)$, $f(2)$, etc., are elements of $X$, so call them $x_1, x_2$, etc. This now looks like a sequence of elements of $X$, so sequences are really just functions from $\N$ to $X$. This notation is standard in mathematics and is frequently used in symbolic dynamics to denote sequence spaces.

Let $E, F$, and $G$ be sets. Then operation on these sets using the intersection and union operators is commutative
\begin{align*}
    E \cap F &= F \cap E \\	
    E \cup F &= F \cup E, 	
\end{align*}

associative
\begin{align*}
    (E \cap F) \cap G &= E \cap (F \cap G) 	\\
    (E \cup F) \cup G &= E \cup (F \cup G), 	
\end{align*}

and distributive
\begin{align*}
    (E \cap F) \cup G &= (E \cup G) \cap (F \cup G) 	\\
    (E \cup F) \cap G &= (E \cap G) \cup (F \cap G). 	
\end{align*}

More generally, we have the infinite distributive laws
\begin{align*}
    A \cap ( \bigcup_{(\lambda \in \Lambda)}B_\lambda) &= \bigcup_{(\lambda \in \Lambda)}(A \cap B_\lambda) 	\\
    A \cup ( \bigcap_{(\lambda \in \Lambda)}B_\lambda) &= \bigcap_{(\lambda \in \Lambda)}(A \cup B_\lambda) 	
\end{align*}

where lambda runs through any index set $\Lambda$. The proofs follow trivially from the definitions of union and intersection.
}

\begin{mydef}
    \label{mydef:1.3}
    If $A$ is any set (whose elements may be numbers or any other objects), 
    we write $x\in A$ to indicate that $x$ is a member (or an element) of $A$.
    \mybox{
        element 还没定义\\    
        object指代什么? 我个人认为集合理解的难点在于集合的集合. 
        % 这一点可以引出罗素悖论
        }
    If $x$ is not a member of $A$, we write: $x\notin A$.

    \emph{empty set} $\varnothing$ contains no element, If a set has at least one element, it is called \emph{nonempty}.

    $A,B$ are sets, 
    $\forall x\in A$, $x\in B$, we say that $A$ is a \emph{subset} of $B$, $A \subset B$ or $B \supset A$. 
    If $\exists x\in B$, $x\notin A$, A is a \emph{proper subset} of $B$, $A \subsetneqq B$.
    Note that $A\subset A$ for every set $A$.

    (Bernstein) If $A\subset B$ and $B\subset A$, we write $A = B$. Otherwise $A \neq B$.
\end{mydef}
\mybox{这条性质在证明集合相等时很常用}

\begin{mydef}
    \label{mydef:1.4}
    Throughout Chap. 1, the set of all rational numbers will be denoted by $\Q $.
\end{mydef}